data preparation

### 2024-09-26 01_data_preparation.Rmd
deleted introduction text

#Introduction
This is the supplementary information of the Master thesis. This document
covers the whole analysis performed to assess response diversity between fish communities
in Swiss peri-alpine lakes. 
This document has two parts: Data preparation (1) and Data analysis (2). 
Function to model general additive models is provided separately (see function_GAM.R). 
Code for figures used in the method figure is also provided separately (see supplementary_method_figure.R)

```{r}
# do we want to include zurich and constance separately?
projet_lac_data <- read.csv("PLDB_final_short_depth_climate_cleantaxa_20052022.csv")

>>>>

#Introduction
Data preparation for analysis.

```{r}
# read in data
projet_lac_data <- read.csv("PLDB_final_short_depth_climate_cleantaxa_20052022.csv")
